Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
major changes to make the paradigm section tick over

In the experiments presented later in this article, we explore the
space of metrics outlined above along multiple dimensions:
\begin{description}
\item[Decompositions]: we consider syntactic decompositions of the
  following types.
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ here, every tuple includes two words
    and the dependency-label between them.
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ the tuple is the word plus the label of the arc
      linking it to its head; this decomposition marks how the word
      fits into its syntactic context (what it modifies).
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ each tuple here is the dependency relation plus
      the word being modified; this decomposition implicitly marks how
      key the word is to the sentence.
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ here, drops the arc-label. This decomposition
      ignores the syntactic-role information implied in the arc labels.
    \item[1g,2g] these decompositions are syntactically-null
      they just includes each 1-gram (or 2-gram) without any
      syntactic labeling at all.  They are thus simple measures of
      unigram (bigram)
      precision and recall.
  \end{description}
\item[Forest size]
Although the parser can generate considerably more, we consider forests of size 1 and of size 50
\item[Forest confidence]
\end{description}

@@

\begin{itemize}

\item Tree features may be extracted from a 1-best tree, or from an
  n-best tree list

  \begin{itemize}
  \item  counts are an expectation over the forest
  \item n parameter: how many trees in the forest
  \item gamma parameter for flattening overconfident parse hyps
  \end{itemize}
  note intentional similarities to Owczarzak paper

\item Components in the basic DPM measures combined in various ways:

  \begin{itemize}
  \item combination of precision, recall scores for different
    components (on analogy with BLEU combination), naive assumption:
    all weighted equally

  \item simple F over items of all valences (naive assumption: all
    weighted equally)
  \end{itemize}
\item Tuneable weights:
  \begin{itemize}
  \item recall that TERp has tuneable system over small number of parameters
    \begin{itemize}
    \item insertion weight
    \item deletion weight
    \item substitution weight
    \item synonym weight (motivated with WordNet)
    \end{itemize}
  \item learn weights for separate precision, recall for various
    components
  \end{itemize}

\item Implementation
  \begin{itemize}
  \item Charniak parser
  \item n=1..50
  \item head-finding, with some modifications
  \item label-construction
  \end{itemize}

>>>>

In the experiments presented later in this article, we explore the
space of metrics outlined above along multiple dimensions:
\begin{description}
\item[Decompositions]: we consider syntactic decompositions of the
  following types.
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ here, every tuple includes two words
    and the dependency-label between them.
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ the tuple is the word plus the label of the arc
      linking it to its head; this decomposition marks how the word
      fits into its syntactic context (what it modifies).
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ each tuple here is the dependency relation plus
      the word being modified; this decomposition implicitly marks how
      key the word is to the sentence.
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ here, drops the arc-label. This decomposition
      ignores the syntactic-role information implied in the arc labels.
    \item[1g,2g] these decompositions are syntactically-null.  They
      simply include each 1-gram (or 2-gram) without any syntactic
      labeling at all.  They are thus simple measures of unigram
      (bigram) precision and recall.
  \end{description}
\item[Forest size]
Although the parser can generate considerably more, we consider forests of size 1 and of size 50.
\item[Forest confidence] An expectation requires a probability distribution over the $n$-best
list, and we consider three options: uniform, the parser
probabilities, and a flattened version of the parser probabilities
such that $\tilde{p}(x) = \frac{p(x)^\gamma}{\sum_ip(i)^\gamma}$
(where $\gamma$ is a free parameter) to account for the fact that the
parser tends to be over-confident.  In all cases, the probabilities
are normalized to sum to one over the the $n$-best list, where the
maximum $n$ in this work is 50.  The uniform distribution ($\gamma =
0$) is intended to be equivalent to the
\cite{owczarzak07labelleddepseval} \textbf{d\_50} and
\textbf{d\_50\_var} measures.\footnote{Since
  \cite{owczarzak07labelleddepseval} report no use of parse
  weights, \textbf{d\_50} and \textbf{d\_50\_var} may be using a sum
  of counts over the 50-best list rather than expected-counts over a
  uniform distribution. These two approaches are equivalent --- so
  long as the $n$-best list is always the same length for hypothesis
  and reference.  In our implementation, the $n$-best list does not
  always reach 50 candidate parses on short sentences, so the
  expectation matches our intent better than a sum of counts over the
  $n$-best.}
\item[score combination]: We consider three possible methods for
  combining scores across decompositions, as suggested in
  section~\ref{sec:approach}:
  \begin{description}
  \item[$F\lbrack\cdot\rbrack$] treats each decomposition as
    contributing $n$ more items to the bag of tokens extracted from
    the tree, ad then computes a global $F$ score.
  \item[$\mu_{PR}\lbrack\cdot\rbrack$] constructs a precision and
    recall score from each decomposition, and then does an
    evenly-weighted harmonic mean of all the component precision and
    recall scores.
  \item Tuned, like the previous combination, calculates precision and
    recall separately for each decomposition, but performs a linear
    weighted combination of the resulting precision and recall scores.
    For this tuning, we note that TERp \cite{snover09terp} provides a
    tuneable system over a small number of parameters (they include,
    among others, separate cost for insertions, deletions,
    substitutions and synonyms) and an optimization algorithm that
    assigns weights to each parameter. We use the various
    decompositions' precision and recall as new parameters to the TERp
    optimizer.
  \end{description}
\end{description}

@@
